Data Analysis Methods for the Detection of the Epoch of Reionization

### 2017-11-28 PAPER.tex
added comparison image between methods and added into text

\newcommand{\cc}[1]{{\color{purple} \textbf{[CC: #1]}}}
\newcommand{\acl}[1]{{\color{red} \textbf{[ACL:  #1]}}}
\newcommand{\dcj}[1]{{\color{orange} \textbf{[DCJ: #1]}}}

@@

Lastly, this method requires that we choose the probability at which we choose to reject the null hypothesis. As can be seen in Figure \ref{fig:Pr_vs_Pin}, the difference between $80$ and $90$\% can mean a difference of almost an order of magnitude in the power spectrum level that is ruled out. We can also see that the probability does not perfectly converge at high injected power levels. \cc{why?} Rather than insist on a rejection at the $99$th percent level, we compromise at $95$\% \dcj{Matt, put in actual value here}.

The resulting limits for inverse covariance weighted PAPER-64 data (the same data used in Method \#1), using this second signal loss method, are shown in Figure \ref{fig:cc_vs_mk} next to the limits from Method \#1. \dcj{Hopefully they are similar!} In the rest of this paper, we use Method \#1 \cc{why?}.

>>>>

\newcommand{\cc}[1]{{\color{purple} \textbf{[CC: #1]}}}
\newcommand{\acl}[1]{{\color{red} \textbf{[ACL:  #1]}}}
\newcommand{\dcj}[1]{{\color{orange} \textbf{[DCJ: #1]}}}
\newcommand{\mjk}[1]{ {\color{olive} \textbf{[MJK: #1]}} }

@@

Lastly, this method requires that we choose the probability at which we choose to reject the null hypothesis. As can be seen in Figure \ref{fig:Pr_vs_Pin}, the difference between $80$ and $90$\% can mean a difference of almost an order of magnitude in the power spectrum level that is ruled out. We can also see that the probability does not perfectly converge at high injected power levels. \cc{why?} Rather than insist on a rejection at the $99$th percent level, we compromise at $90$\% \dcj{Matt, put in actual value here} \mjk{The current image uses 90th percentile!}.

The resulting limits for inverse covariance weighted PAPER-64 data (the same data used in Method \#1), using this second signal loss method, are shown in Figure \ref{fig:sigloss_compare} next to the limits from Method \#1. \dcj{Hopefully they are similar!} In the rest of this paper, we use Method \#1 \cc{why?}.

\begin{figure}[t]
\centering
\includegraphics[width=.4\textwidth]{plots/sigloss_method_comparison.png}
\caption{A comparison of Method \#1 
signal loss corrected power spectrum (black dots)
and Method \#2 uppers limits at 90\% confidence (red curve).
Also shown are the upper limits of the unweighted power spectrum
(blue dashed) and theoretical noise model (green). \label{fig:sigloss_compare} }
\end{figure}
